On the presentation of orthogonal groups over polynomial rings

### 2019-08-02 dl-paper.tex
Proving 5.30

\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s) x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

@@

\begin{lemma}
For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
\end{lemma}
\begin{proof}
 It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ ($f \in M[X]$, $\xi\in A[X]$).
 %Notice that in the case $\xi = 0$ the assertion immediately follows from~\eqref{T_leq0} since $t(x_\alpha(f)) = x_\alpha(f)$. 
 We verify the assertion by induction on the degree of $\xi$ in $X$.

@@

\begin{multline}
 z_{\alpha+\beta}(f, ax) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
\end{multline}

>>>>

\item\label{Z4} $z_{\beta}(s, \xi) ^ {x_{\alpha}(\eta)} = z_{\beta}(s, \xi)\ \text{if}\ \alpha\perp\beta$;
\item\label{Z5} If $\alpha+\beta\in\Phi$, then holds:
\begin{multline} \nonumber z_{\alpha+\beta}(s\eta, \xi) = x_\alpha(\epsilon s)\cdot x_{-\beta}(-s\xi) \cdot x_{\beta}(s\xi\eta^2) \cdot x_{\alpha+\beta}(s \eta) \cdot \\ \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta) \cdot
  x_{-\alpha}(-\epsilon s\xi^2\eta^2) \cdot x_{-\alpha-\beta}(- s \xi^2 \eta) \cdot z_{-\beta}(s\xi, -\eta)\text{ where $\epsilon = N_{\alpha,\beta}$.}\end{multline}
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}, so it remains to verify the last assertion.
Direct computation shows that
\begin{multline} \nonumber
  z_{\alpha+\beta}(s\eta, \xi) = [x_\alpha(\epsilon s)^{x_{-\alpha-\beta}(\xi)}, x_\beta(\eta)^{x_{-\alpha-\beta}(\xi)}] =
  [x_\alpha(\epsilon s) x_{-\beta}(-s\xi), x_{\beta}(\eta) x_{-\alpha}(\epsilon \xi\eta)] = \\ 
  = x_\alpha(\epsilon s) \cdot x_{-\beta}(-s\xi) \cdot z_\alpha(-\epsilon s, -\epsilon \xi\eta)^{x_{\beta}(-\eta)} \cdot z_{-\beta}(s\xi, -\eta)^{x_{-\alpha}(-\epsilon \xi\eta)},
\end{multline} 
and the required assertion follows from~\eqref{Z2}.
\end{proof}

@@

\begin{lemma}
For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
\end{lemma}
\begin{proof}
 It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
 Set $I = M[X, X\inv]$. It is not hard to verify the assertion for the element $g_1 = z_\alpha(X^2f, aX^{-1}) \in \St(\Phi, B, I)$.
 Indeed, using the fact that $x_{\alpha}(X^2f) \in P_{-\alpha}(0)$ we obtain that
 \begin{multline}
  g_1 \cdot (g, [h], u) = x_{-\alpha}(-aX^{-1}) (x_\alpha(X^2f)x_{-\alpha}(aX^{-1})g, [h \cdot x_{-\alpha}(\tfrac{-aX^{-1}}{1+am})] )
\end{multline}

   \[ g_1 \cdot (g,\ [h],\ u) = () \]
 Consider the case $\xi = aX^{-1}$, $f = X^2f'$

 We verify the assertion by induction on the degree of $\xi$ in $X$ starting from $-1$.

@@

\begin{multline}
 z_{\alpha+\beta}(f, aX) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
\end{multline}
